% ************************** Thesis Acknowledgements **************************
\begin{acknowledgements}      
    
    There are many people and organizations I would like to thank during the four years I have taken to complete my PhD.
    
    First, the official acknowledgments.
    To start with the people who created and maintain the telescopes and instruments who made this research possible.
    SDO/AIA and SDO/HMI data are used courtesy of NASA/SDO and the AIA and HMI science teams.
    The Swedish 1-m Solar Telescope is operated on the island of La Palma by the Institute for Solar Physics of Stockholm University in the Spanish Observatorio del Roque de los Muchachos of the Instituto de Astrofsica de Canarias.
    I want to thank Luc Rouppe van der Voort (Institute of Theoretical Astrophysics, University of Oslo) and J. de la Cruz Rodriguez (University of Uppsala, Sweden) for data reductions with MOMFBD for SST/CRISP.
    DST/ROSA and DST/IBIS data used in this thesis were obtained with the facilities of the National Solar Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc.
    The DOT was operated by Utrecht University (The Netherlands) at Observatorio del Roque de los Muchachos of the Instituto de Astrofsica de Canarias (Spain) funded by the Netherlands Organisation for Scientific Research NWO, The Netherlands Graduate School for Astronomy NOVA, and SOZOU.
    The DOT efforts were part of the European Solar Magnetism Network.
    The SVST was operated by the Institute for Solar Physics, Stockholm, at the Observatorio del Roque de los Muchachos of the Instituto de Astrofísica de Canarias (La Palma, Spain).
    To finish, the computational tools and packages I used to analyze the data provided, AstroPy \citep{theastropycollaboration2013}, Ginga, IPython \citep{perez2007}, Matplotlib \citep{hunter2007}, NumPy \citep{jones2001}, SciPy \citep{jones2001}, scikit-image \citep{vanderwalt2014}, SolarSoft \citep{1998SoPh..182..497F}, SunPy \citep{thesunpycommunity2015a} and SymPy \cite{sympydevelopmentteam2014}
    I want to thank J. Terradas for providing the EMD routines used in the data analysis.
    Wavelet power spectra were calculated using a modified computing algorithms of wavelet transform original of which was developed and provided by C. Torrence and G. Compo, and is available at URL: \url{http://paos.colorado.edu/research/wavelets/}.
    The Science and Technology Facilities Council (STFC) funded my PhD and my travels around Europe.
    
    Second, the people I have meet and worked with during my PhD.
    I would like to thank Steven Christie for inviting me to give a talk at NASA GSFC (even if it did not go down very well).
    Alex for his countless help with MHD theory.
    Chris (and Helen by extension), for helping me throughout my PhD.
    Without his ability to encourage me and his technique for fine writing and science, I would have been very lost and I want to thank you for out doing me at every turn.
    I want to also thank Chris's seven papers for getting him two jobs thus keeping him around for Freddie for another two years.
    Tom, for his ability to ignore me whenever I say hello, I have never been so insulted in my entire life.
    Freddie, for those gains, the numerous nights out and his bitching talk at NASA GSFC.
    Stevie, for his inability to eat nice food which has provided many hours of entertainment and his incredible ability to eat an entire loaf of bread in a single sitting. 
    Stuart, for all that Python support he provided me, without which my papers would have been very barren.
    Sky (and Beth by extension), for letting me annoy them for 4 years (or was it just 3 months?) with my grating personality.
    It was an honour for me to be a groomsman for your wedding and long may your marriage continue.
    I want to thank my fountain pen collection for being there through thick and thin (thanks Freddie).
    The office has been a fantastic environment, through the magic craze, the ball games, the breaking incidents and the antics of Freddie. 
    I do apologize for the loudness that I have caused.
    But I can say without hesitation, that it has been the best four years so far in my life and I have met some truly amazing human beings.
    Sorry that I can not include everyone by name but I want to thank everyone else that I have had the pleasure of meeting during my PhD.
        
    I would like to thank my PhD supervisor Robertus Erd\'elyi.
    Without him giving me the chance to do this PhD, I would be doing some sort of normal boring job.
    He believed in me and gave me this opportunity, which I am very grateful for.
    He has been a fantastic supervisor, encouraging me to push myself and has been patient at the times I have been slow or stupid.
    
    Last but not least, my family.
    I want to thank my mother and sister supporting me through my time at Sheffield.
    It as always been a comfort to know that I can go back whenever I needed to.
    I'll be home soon.
    
\end{acknowledgements}